\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-05-09 article/article.tex
use \in instead of :

\subsection{Model Predictive Control}\label{ssec:MPC}
Consider a system composed of discrete-time linear time-invariant agents ${i\in\set{M}=\{1\mathbin{:}\nsubsystems\}}$, modeled by
\begin{equation}
\begin{matrix}
  \label{eq:systems}
\vec{x}_{i}[k+1]&=&A_{i}\xik &+& B_{i}\uik\\
\vec{y}_{i}[k+1]&=&C_{i}\xik &&
\end{matrix},
\end{equation}
with $\vec{x}_{i}[k]:\R^{n_{x}}$, $\vec{u}_{i}[k]:\R^{n_{u}}$ and $\vec{y}_{i}[k]:\R^{n_{y}}$.

Each agent's input $\uik$ is constrained by
\begin{equation}
  \label{eq:u_local_constraints}
  \0_{n_{u}}\preceq\uik\preceq\vec{u}_{\max},
\end{equation}
with ${\umax:\R^{n_{u}}}$.
The agents are coupled by global input constraints with weighting matrices ${\Gamma_{i}:\semidefpos^{n_{u}}}$:
\begin{equation}
  \label{eq:global_constraint}
  \sum_{i\in\set{M}}\Gamma_{i}\uik\preceq\umax.
\end{equation}

@@

\end{matrix}
  $}
% \label{eq:dmpcModLOP}
\end{equation}
where ${Q_{i}:\semidefpos}$, ${R_{i}:\defpos}$, and $\vik$ is a control objective.
$\optglobobj$ denotes the optimal value of the objective function for the optimal control sequences ${\optuiseq}$.
The problem in~\eqref{eq:GOP} is solved at each time $k$, and the ${\optuikk}$ are applied in their respective subsystem $i$, following a \rhs{}.

@@

The \emph{local problems}~\eqref{eq:DOP_local} can be rewritten in a equivalent (same solution) constrained \qp{} form:
  \begin{subequations}\label{eq:quadratic_case}
    \begin{align}
      \label{eq:4}
      \underset{\Uik}{\mathrm{minimize}}&&\small J_{i}(\vec{\theta}_{i})=&\frac{1}{2} \Uik^T H_i\Uik +{\fik}^T\Uik\\
      \mathrm{subject~ to}&&&\bar{\Gamma}_{i}\Uik\preceq\vec{\theta}_{i}[k]:\vec{\lambda}_{i}[k]\label{eq:constraints}\\
                                        &&&\Uik\succeq\0_{c},
    \end{align}
  \end{subequations}
where ${\Uik}$ stacks the input prediction sequences, and
${\bar{\Gamma}_{i}=\kron{I_{\predhorz}}{\Gamma_{i}}}$.
The values for $H_{i}$ and $\vec{f}_{i}[k]$ vary depending on the control objective $\vec{v}_{i}[k]$. The approach presented in this paper does not depend on the choice of the control objective.
The approach depends only on the fact that ${H_{i}:\semidefpos}$ does not depend on $k$, while $\fik$ does. Those facts are instrumental for the results in the following sections.

@@

 As each constraint can be active or inactive, for a given group of $t$ constraints, we can have at most $N=2^{t}$ different combinations of active sets.

@@

As \eqref{eq:linear_cheating_random} is a \pwa{} function whose modes depend on the unknown zone ${z\in\set{Z}}$,
we associate to each couple $(    \randomvec{\lambda}_{o}, \randomvec{\theta}_{o})$ a latent unobserved random variable ${\random{z}_{o}}$ that indicates in which zone in $\set{Z}$ the observable variables were obtained.
These variables are organized in ${\random{Z}:\R^{1\times O}}$ which is our set of latent variables $\set{U}$.

>>>>

\subsection{Model Predictive Control}\label{ssec:MPC}
Consider a system composed of discrete-time linear time-invariant agents ${i\in\set{M}=\{1\mathbin{:}\nsubsystems\}}$, modeled by
\begin{equation}
\begin{matrix}
  \label{eq:systems}
\vec{x}_{i}[k+1]&=&A_{i}\xik &+& B_{i}\uik\\
\vec{y}_{i}[k+1]&=&C_{i}\xik &&
\end{matrix},
\end{equation}
with ${\vec{x}_{i}[k]\in R^{n_{x}}}$, ${\vec{u}_{i}[k]\in R^{n_{u}}}$ and ${\vec{y}_{i}[k]\in R^{n_{y}}}$.

Each agent's input $\uik$ is constrained by
\begin{equation}
  \label{eq:u_local_constraints}
  \0_{n_{u}}\preceq\uik\preceq\vec{u}_{\max},
\end{equation}
with ${\umax\in R^{n_{u}}}$.
The agents are coupled by global input constraints with weighting matrices ${\Gamma_{i}\in\semidefpos^{n_{u}}}$:
\begin{equation}
  \label{eq:global_constraint}
  \sum_{i\in\set{M}}\Gamma_{i}\uik\preceq\umax.
\end{equation}

@@

\end{matrix}
  $}
% \label{eq:dmpcModLOP}
\end{equation}
where ${Q_{i}\in\semidefpos}$, ${R_{i}\in\defpos}$, and $\vik$ is a control objective.
$\optglobobj$ denotes the optimal value of the objective function for the optimal control sequences ${\optuiseq}$.
The problem in~\eqref{eq:GOP} is solved at each time $k$, and the ${\optuikk}$ are applied in their respective subsystem $i$, following a \rhs{}.

@@

The \emph{local problems}~\eqref{eq:DOP_local} can be rewritten in a equivalent (same solution) constrained \qp{} form:
  \begin{subequations}\label{eq:quadratic_case}
    \begin{align}
      \label{eq:4}
      \underset{\Uik}{\mathrm{minimize}}&&\small J_{i}(\vec{\theta}_{i})=&\frac{1}{2} \Uik^T H_i\Uik +{\fik}^T\Uik\\
      \mathrm{subject~ to}&&&\bar{\Gamma}_{i}\Uik\preceq\vec{\theta}_{i}[k]:\vec{\lambda}_{i}[k]\label{eq:constraints}\\
                                        &&&\Uik\succeq\0_{c},
    \end{align}
  \end{subequations}
where ${\Uik}$ stacks the input prediction sequences, and
${\bar{\Gamma}_{i}=\kron{I_{\predhorz}}{\Gamma_{i}}}$.
The values for $H_{i}$ and $\vec{f}_{i}[k]$ vary depending on the control objective $\vec{v}_{i}[k]$. The approach presented in this paper does not depend on the choice of the control objective.
The approach depends only on the fact that ${H_{i}\in\semidefpos}$ does not depend on $k$, while $\fik$ does. Those facts are instrumental for the results in the following sections.

@@

 As each constraint can be active or inactive, for a given group of $t$ constraints, we can have at most ${N=2^{t}}$ different combinations of active sets.

@@

As \eqref{eq:linear_cheating_random} is a \pwa{} function whose modes depend on the unknown zone ${z\in\set{Z}}$,
we associate to each couple $(    \randomvec{\lambda}_{o}, \randomvec{\theta}_{o})$ a latent unobserved random variable ${\random{z}_{o}}$ that indicates in which zone in $\set{Z}$ the observable variables were obtained.
These variables are organized in ${\random{Z}\in\R^{1\times O}}$ which is our set of latent variables $\set{U}$.
